Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-24 journal paper/content/sec-intro.tex
A few more edits re Ian's comments.
Expanded a footnote.

Each principal faces a basic and well-studied version of the multi-armed bandit problem, where each reward is drawn independently from a fixed, action-specific distribution. Each principal's strategy is a bandit algorithm; as such, it can dynamically adjust itself to the observed rewards, but not to the competition. This modeling choice reflects the reality of industrial applications, which build on a huge body of knowledge in machine learning; more on this in Section~\ref{sec:discussion}.
%Responding to the competition is another layer of complexity which has not been previously studied in this context, let alone made practical.
We draw on the machine learning literature to compare bandit algorithms to one another \asedit{in isolation},%
\footnote{\asedit{As opposed to ``in competition", as solutions to a stand-alone exploration problem without competition.}}
 so that we can talk about \emph{better} bandit algorithms in a principled way.
%\footnote{Such comparisons are somewhat subtle, as some algorithms may be better for some problem instances and/or time intervals, and worse for some others. More on this in Appendix~\ref{app:bg}. Generally,  ``better" algorithms are better in the long run, but could be worse initially. }
One baseline is algorithms that do not explicitly explore (\emph{greedy algorithms}); \asedit{in isolation}, they are known to be terrible for a wide variety of problem instances.

@@

\textbf{(ii)} We dilute the \HardMax agents with a small fraction of ``random agents" who choose a principal uniformly at random. We call this model \HardMaxRandom. Then better algorithms help in a big way: a sufficiently better algorithm is guaranteed to win all non-random agents after an initial learning phase. There is a caveat, however: any algorithm can be defeated by interleaving it with the greedy algorithm. This has two undesirable consequences: a better algorithm may sometimes lose in competition, and a pure Nash equilibrium typically does not exist.

>>>>

Each principal faces a basic and well-studied version of the multi-armed bandit problem, where each reward is drawn independently from a fixed, action-specific distribution. Each principal's strategy is a multi-armed bandit algorithm; as such, it can dynamically adjust itself to the observed rewards, but not to the competition. This modeling choice reflects the reality of industrial applications, which build on a huge body of knowledge in machine learning; more on this in Section~\ref{sec:discussion}.
%Responding to the competition is another layer of complexity which has not been previously studied in this context, let alone made practical.
We draw on the machine learning literature to compare bandit algorithms to one another \asedit{in isolation},%
\footnote{\asedit{As opposed to ``in competition": as solutions to a stand-alone exploration problem which aims to maximize the total consumer welfare over time (see Appendix~\ref{app:bg} for self-contained backround).}}
 so that we can talk about \emph{better} bandit algorithms in a principled way.
%\footnote{Such comparisons are somewhat subtle, as some algorithms may be better for some problem instances and/or time intervals, and worse for some others. More on this in Appendix~\ref{app:bg}. Generally,  ``better" algorithms are better in the long run, but could be worse initially. }
One baseline is algorithms that do not explicitly explore (\emph{greedy algorithms}); \asedit{in isolation}, they are known to be terrible for a wide variety of problem instances.

@@

\textbf{(ii)} We dilute the \HardMax agents with a small fraction of ``random agents" who choose a principal uniformly at random. We call this model \HardMaxRandom. Then better algorithms help in a big way: a sufficiently better algorithm is guaranteed to win all non-random agents after an initial learning phase. There is a caveat, however: any algorithm can be defeated by interleaving it with the greedy algorithm. This has two undesirable consequences: a better algorithm may sometimes lose in competition, and a Nash equilibrium typically does not exist.
